Generalized Tractability

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

\section{Sub-$h$ Tractability}\label{sec:subh}
In this section we generalize the concept of weak tractability \cite{}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
\begin{equation} \label{eq:h_cond}
	h \text{ is strictly increasing}, \qquad 
	h(0)=1, \qquad  
 h(x+y) \ge  h(x)\cdot h(y)  \quad \forall x,y \ge 0.
\end{equation}
This means that $\log(h(\cdot))$ is a superadditive function.  The function $h$ here can be thought of as the exponential function for weak tractability.

>>>>

\section{Sub-$h$ Tractability}\label{sec:subh}
In this section we generalize the concept of weak tractability \cite{}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
\begin{equation} \label{eq:h_cond}
	h \text{ is strictly increasing}, \qquad 
	h(0)=1, \qquad  
 h(x+y) \ge  h(x)\cdot h(y)  \quad \forall x,y \ge 0.
\end{equation}
This means that $\log(h)$ is a superadditive function.  An example of the function $h$ is the exponential function, from which we can recover weak tractability.
